\documentclass[letterpaper,10pt,titlepage]{article}

% This might mess up formatting
\setlength{\parindent}{0pt}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}

\usepackage{alltt}
\usepackage{float}
\usepackage{color}
\usepackage{url}
\usepackage{listings}
\usepackage{biblatex}
\usepackage{filecontents}

\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}

\usepackage{geometry}
\geometry{textheight=8.5in, textwidth=6in}

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{pgfgantt}

\lstdefinestyle{customc}{
  belowcaptionskip=1\baselineskip,
  breaklines=true,
  frame=L,
  xleftmargin=\parindent,
  language=C,
  showstringspaces=false,
  basicstyle=\footnotesize\ttfamily,
  keywordstyle=\bfseries\color{green!40!black},
  commentstyle=\itshape\color{purple!40!black},
  identifierstyle=\color{blue},
  stringstyle=\color{orange},
}

\def\name{Brandon Lee}

%pull in the necessary preamble matter for pygments output
% \input{pygments.tex}

%% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {CS461 ``Senior Capstone''},
  pdftitle = {CS 461 Progress Report},
  pdfsubject = {CS 461 Progress Report},
  pdfpagemode = UseNone
}

\begin{document}

\begin{titlepage}
    \begin{center}
        \vspace*{3.5cm}

        \textbf{Progress Report}

        \vspace{0.5cm}

        \textbf{Brandon Lee, Rutger Farry, Michael Lee}

        \vspace{0.8cm}

        CS 461\\
        Fall 2016\\
        7 December 2016\\

        \vspace{1cm}

        \textbf{Abstract}\\

        \vspace{0.5cm}

		The purpose of this document is to elaborate the details of the current status of our application, C7FIT. The following document will consist of four core parts discussing areas of design in the development of our application including a purpose and goals recap, current status, problems, and retrospective.
        \vfill

    \end{center}
\end{titlepage}

\newpage

\tableofcontents

\newpage

\section{Purpose and Goals Recap}

In mid 2017, eBay will launch a mobile application for a local Portland based fitness gym, Club Seven Fitness. This application will serve as a fitness application to allow users and gym-goers to enroll in classes and record fitness data. This data will be tied with Club Seven's existing API platform, MindBody.\\

Completion goals for this application include finishing a production version by the end of the school year with hopes of pushing to the Apple App store.

\section{Current Status}

Currently, designs and documentation are completed for the most part, however very little coding has been done so far. There is still much work to do in that front. We will start sometime during winter break to get a head start on things.

\section{Problems}

Over the course of the term we have only been planning and writing design documents, and while these are necessary to complete our project  we need to actually start coding the project if we want to finish our goals by the end of the year. We're currently missing some required resources that we need to work on our project: we haven't received access to the MindBody API developer account that we need.
Thankfully, communication between our client has been prompt with responding to our needs and we haven't been able to start coding the project regardless. We will be working on the project over Winter Break in order to hopefully finish on time. \\


Some re-occurring problems throughout the term were difficulties in balancing other classes with the requirements of this project, as the longevity of this project makes it easy to put off; However, the plans that we've been required to make will help us maintain our schedule in addition to the work time we'll have reserved next term. We have also been struggling with some of the requirements from the writing assignments. The expectations were unclear on many of the assignments, which lead to confusion and we came close to the deadlines.



\section{Retrospective}

\textbf{10/14/16}\\

Brandon Lee\\

Problems\\
Communication was a bit rough as clients and students were using email for half of the week before switching to Slack.
Additionally clients and students have not met up in person yet to discuss details of the project, so as of right now some details are still vague due to the broad scope of specifications.\\

Progress\\
Wrote Problem Statement.
Created GitHub Organization and repo.
Created Slack for remote communication.\\

Plans\\
Next week Wednesday we are planning to go up to Portland to discuss further details about the app with clients at eBay in person.
I plan to catch up on learning up a bit on some iOS concepts in the extra time before we formally begin.\\

Michael Lee\\

The progress of this week has kept up with the pace of this class. Last week we had the first phone meeting with our client where we hashed out the basics details of our project. We had a group meeting after that to work out the details of our problem statement.\\

Overall the communication between our group and client were good. It was slightly difficult because they are remote, however we had good email communication and we set up a slack to help. There were some miscommunications due to online communication when getting our signatures, however because our client responded promptly we were able to complete the assignment on time.\\

Our group plans to go up to Portland to meet with our client next week Wednesday so we can talk about the app in detail and meet the team that were going to work with. As I haven’t really worked in depth with IOS programming, I will need to catch up to my teammates and so I plan on learning some IOS in the coming week.\\

Rutger Farry\\

This week was focused on battening down the hatches on what our final product is going to look like. Up until last Friday, I only knew the platform and language our program would be implemented in. I had no idea what it would actually do, what it should look like, etc.\\

I now understand we will be producing a fitness app for iOS that connects to the Mindbody platform to communicate workouts between clients and coaches. We narrowed down the problem we'd be addressing in our Problem Statement, drew up wireframes, and began investigating what libraries we should use for things such as API calls, layouts, data management, etc.\\

Next week we will be driving up to Portland to meet with our team in the eBay offices, and should be able to begin work on the app. I'd like to get the structure outlined completely in code, and perhaps begin on some API calls. Looking forward to see what we can get done!\\

\textbf{10/21/16}\\

Brandon Lee\\

Problems\\

Since we're still just ramping up, currently still blocked on not having an exact direction to proceed in terms of app architecture and design. Need to confirm major requirements in accordance with these core principles. Will be sitting down with fellow students this weekend and discussing this weekend.
Communication still seems to be slow as not many people (clients and students) seem to be using the Slack, so communication as of currently is still just a mixture of emails and Slack.\\

Progress\\

Visited eBay Portland in person to discuss details and iron out plans.
Got a clearer idea of what is required by the clients in terms of app functionality and features.
Created a resources page with useful links.
Received back Problem Statement, will update and turn in by Monday.\\

Plans\\
Develop requirements document by next week.
Sit down with team and discuss higher level app architecture.
Create Sketch mockup design of app.
Continue reading up on iOS.

Michael Lee\\

Our team hasn't had too many problems, as we've already met with our client twice. Our biggest problem would be working on the next requirements document and determining what is feasible in the time we have, as from the meetings we've had the project seems quite large.\\

On Wednesday we went up to Portland to meet with our client eBay. They showed us around their office and we were able to meet the team members we will be working with. During the meeting we discussed what technologies we will be using on our app and the look of each of the menus. We received our edited Problem statement Thursday night and we'll be revising that later this week.\\

For the future, we need to iron out a more official requirements document. Even though we have a preliminary version, we need to be clear on the particular functions. To do this we'll be using the rough wireframes that Luther provided us and our initial requirements document.\\

Rutger Farry\\

The highlight of this week was traveling to Portland and visiting the people at eBay's office that we'd be working with. We had a good high-level talk about the app's purpose and later drilled down into the specific requirements, with a more extensive functional requirements doc promised soon.\\

I now feel like we're nearing the level of confidence in the app's direction that we'll be able to start coding soon. The next steps we take are mostly to improve the quality of the code we write. Things like setting up continuous integration and developing UI redlines to create consistent expectations across team members and to ensure that those expectations are met. We will probably be focusing on this, along with writing / revising the class's homework documents before moving on to code.\\

\textbf{10/28/16}\\

Brandon Lee\\

Problems\\
Busy week for both students and clients. Was not able to obtain an updated list of functional requirements until Thursday night, the night before the Requirements Document rough draft due.
Difficulty organizing time to collectively work together as students on Problem Statement and Requirements Document due to scattered midterm schedules.
Communication on Slack still not very strong between students and client.\\

Progress\\
Hammered out final copy of Problem Statement as well as rough draft for Requirements Document.
Got in more communication between students on Slack.
Got more communication with clients through email.
Laid out a bit of the technical designs (higher level architecture, data flow).\\

Plans\\
Develop Sketch designs from wireframes
Layout more architecture/design
Continue reading up on iOS.\\

Michael Lee\\

This week we were able to complete our requirements doc on time, but our team was a little strapped for time. Most of our team was busy throughout the week, so most of the requirements doc was done close to the deadline.\\

This process for this week was mainly just the creation of the requirements document. We did get a list of functional requirements from our client, however it was too late to be implemented into the current iteration of our requirements document. As a team we met to talk about some of the higher level design of the app, which will be useful for when we create the design document.\\

For the coming week we need to finalize our requirements document and continue to work on the higher level design of our application.\\

Rutger Farry\\

We're getting into the thick of midterm season, which I think has everyone a little stretched. Most of our efforts this week were focused on getting our Requirements Document written and our Problem Statement revised. Working on the requirements document actually encouraged us to get some useful work done on designing our application architecture, however. I'm excited that we finally started drilling down into this and am excited to explore some of the decisions we made in the area of functional reactive programming and unidirectional dataflow in Swift.\\

The team has additionally been looking into where we want the UI design to go, but it hasn't progressed much beyond high-level discussions and looking at design inspirations. Hopefully as midterms start to wind down we can start laying down the foundation of the app.\\

\textbf{11/4/16}\\

Brandon Lee\\

Problems\\
Design and functionality is a bit broad at this time.
Client wanted to obtain first draft of design in Sketch.

Progress\\
Got initial sketch designs implemented and sent to client.\\

Plans\\
Plan and write Technology Review and Implementation Plan
Continue reading up on iOS.\\

Michael Lee\\

This week we didn't do much as a group and I had two midterms to deal with, so the progress on capstone was stagnated.\\

For next week we need to get together as a group and plan our technology review and Implementation plan\\

Rutger Farry\\

Progress is coming along well on the design and I feel that we have a very solid foundation to move forward on. We've written several design documents planning out the different stages of our implementation and have considered how to construct the different components of our app and how they will interact. With midterms winding down for me, I'm looking forward to starting to implement the app.\\

\textbf{11/11/16}\\

Brandon Lee\\

Problems\\
Busy week for both students and clients. Was not able to obtain feedback on initial sketch designs.
Technology Review and Implementation Plan seldom planned or started at this time.\\

Progress\\
Met together as students and laid out design for what we wanted to do with the document.\\

Plans\\
Write Technology Review and Implementation Plan
Continue reading up on iOS.\\

Michael Lee\\

Personally, I'm more inexperienced than my other group members in IOS programming, so the implementation document requires more research for me to complete my section.\\

Our team met up and we discussed the implementation document, and have begun researching the different technologies we can use to complete our project.\\

For the next week I need to finish researching and writing the document so that it is complete by Monday.\\

Rutger Farry\\

We've started work on another document – a technology review to further explore possible implementation plans for the components that make up our app and to choose the best option. In my opinion, the best way to do this is to just start writing something with that library / architecture. The time constraints for the document make it impossible to do this effectively however, so we are just reading blog posts and software documentation from Apple instead.\\

Both us and our sponsors are excited for us to begin implementing our app, but most our work has gone into writing our documents however.\\

\textbf{11/18/16}\\

Brandon Lee\\

Problems\\
Schoolwork is piling up and getting busier.
Communication between students and client seem to be getting sparse.\\

Progress\\
Wrote and completed Technical Document

Plans\\
Plan and write Design Document
Continue reading up on iOS.\\

Michael Lee\\

Progress\\
This week we completed the technology review early in the week. We also met up to make some preliminary plans for our Design document.\\

Problems\\
With midterms from other classes, it's hard to coordinate with group members, and it's unclear what we need to do for the design document\\

Plans\\
Continue to make progress on the design document\\

Rutger Farry\\

This week was mostly coasting. We worked on our technical requirements doc and have started looking into the design doc. We've had a bit of communication with eBay about our mockups, but besides that haven't talked with them much. I've been working on some side iOS projects and have a good idea about how I'd like to implement state management in our app.\\

\textbf{11/25/16}

Brandon Lee\\

Problems\\
Schoolwork is piling up and getting busier.
Thanksgiving Break\\

Progress\\
Not much currently due to holiday week.\\

Plans\\
Pick up where we left off last week after holidays.\\

Progress\\
We haven't made any progress this week due to the holidays.\\

Problems\\
We didn't make any progress this week.\\

Plans\\
We plan to work on the design document next week.\\

Michael Lee\\

Progress\\
We haven't made any progress this week due to the holidays.\\

Problems\\
We didn't make any progress this week.\\

Plans\\
We plan to work on the design document next week.\\

Rutger Farry\\

This week was mostly spent eating turkey. I also ate some other things. Didn't do much related to the app.\\

\textbf{12/2/16}

Brandon Lee\\

Problems\\
Design Document not done.\\

Progress\\
We completed Document.\\

Plans\\
Wrap up this week and finish strong with finals next week!\\

Michael Lee\\

Progress\\
We completed our design document and turned it in without a signature, as we completed it late Thursday we didn't have time to get our client to sign it.\\

Problems\\
The expectations of the design document were very unclear going into it so it took much longer to complete than expected.\\

Plans\\
Start working on the Progress Report\\

Rutger Farry\\

This week we worked on our design document along with the myriad of other homeworks we had assigned. We ended up writing quite a lot and turned it in Friday morning. We're looking forward to using the lack of homework over Christmas break to start working on the app.\\

\newpage

\section{Signed Participants}

\textbf{Students}

Brandon Lee\\
Rutger Farry\\
Michael Lee\\

\end{document}
