\subsection{Tech Document Changes}
The biggest change we encountered throughout our project was removing usage of the MINDBODY API from our feature list. This actually had a relatively low impact on our technology choices, and if anything simplified our decision-making. Since MINDBODY was a SOAP-based XML API that lacked a Swift wrapper, implementing MINDBODY in our app would require using a library for making HTTP calls, as well as an XML parsing library, for parsing the results of those calls. We considered this and spent a good deal of effort evaluating different options while writing our original tech document. However, in the end, almost our entire web stack was based on Firebase (which has a native Swift library). We only had to use an HTTP library for interacting with the eBay API and did not have to make use of an XML parsing library at all.

There was only one other major change from our original tech document, and that was the removal of a reactive library from our application. In our original document, we had considered using a reactive library such as RxSwift or ReactiveCocoa for our application to help manage our data and keep our UI in sync with our app's state. In the end, we found that Firebase provided a lot of this functionality out of the box, and decided we did not want to bring in an additional external dependency. For sections that used the eBay API, we just went with a more classic imperative model. Since the functionality was pretty simple, we just built some basic tests and did not run into any problems in that area.